\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/0_abstract.tex
Update final details
Add Elke comments; squeeze for 1st submission

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints, i.e. mutual exclusion between clusters. We then prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze. 
An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g. robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments. 
% and by predicting edge weights with a CNN. 
We then show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset. 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints. We prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze. An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g. robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset. 
\end{abstract}

### 2019-05-23 chapters/1_intro.tex
Add Elke comments; squeeze for 1st submission

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of using signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms were proposed. 
% Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.

Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient. Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g. robustness and efficiency.

@@

We evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework.
% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.95\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model. \textbf{(3)} Outputs of three different agglomerative algorithms included in the proposed generalized framework. The  agglomeration order in (a) shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). The final clustering / instance segmentation is shown in (b). We also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of using signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms have been proposed. 
% Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.

Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient. Despite the fact that there exists a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g. robustness and efficiency.

@@

We evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}). 
% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})

@@

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.85\textwidth]{./figs/intro_image_v2.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our UNet model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of three different agglomerative algorithms included in our proposed generalized clustering framework. The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown), or never (black). The final clustering / instance segmentation is shown in 3c, overlaid with the raw image. In 3a, we also illustrate some iterations of the algorithms on toy graph examples with attractive (green) and repulsive (red) interactions.
%We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-23 chapters/3_algorithm.tex
Add Elke comments; squeeze for 1st submission

\section{Generalized Framework for Agglomerative Clustering of Signed Graphs} \label{sec:general_framework}
In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec. \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec. \ref{sec:alg_update_rules}).
 % introduces the proposed generalized framework: 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
% we  in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in  and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in .

@@

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms \UPDATE{REFS} for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

@@

\subsection{\algname{}: Generalized Algorithm for Agglomerative Signed Graph Partitioning} \label{sec:algorithm}

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l ? c | c | c}
            % \toprule\toprule
            \multicolumn{3}{c?}{\multirow{2}{*}[-0.5em]{\thead{\textbf{}}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c?}{} &  &  \multicolumn{1}{c|}{\thead{No Constraints}} & \thead{With Constraints} \\

            \midrule[0.3em]
            % \cmidrule[0.3em]{2-6}
            % \morecmidrules \cmidrule[0.15em]{2-6}
            % \midrule \midrule
            \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ 
            % \cmidrule[0.07em]{2-6}

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The average linkage without cannot-link constraints returned the best segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see bottom panel of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}} and Table \ref{tab:linkage-criteria}, unsigned graphs).

>>>>

\section{Generalized framework for agglomerative clustering of signed graphs} \label{sec:general_framework}
In this section, we first define notation and then introduce one of our main contributions: a signed graph partitioning algorithm (Sec. \ref{sec:algorithm}) that can be seen as a generalization of several existing and new clustering algorithms (Sec. \ref{sec:alg_update_rules}).
 % introduces the proposed generalized framework: 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
% we  in Sec.~\ref{sec:notation}, introduce Algorithm \ref{main_alg} in  and finally show how it can be seen as a generalization of existing and new graph clustering algorithms in .

@@

We consider an undirected simple edge-weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. In computer vision applications, the nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} or \emph{partitioning} with $K$ clusters if $V = \cup_{S\in\Pi} S $, $\,S \cap S' = \emptyset$ for different clusters $S, S'\in \Pi$ and every cluster $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. We also denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}
% In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. 
The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates to every edge a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that other formalisms for positively weighted graphs associate distances to the edges, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates to each edge a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring positive and negative edge weights $\cost_e\in \mathbb{R}$. Following the theoretical considerations in \cite{lange2018partial}, we define these signed weights as ${\cost_e = w_e^+ - w_e^-}$. Some approaches directly compute $\cost_e$, whereas others compute $w_e^+$ and $w_e^-$ separately.
In this formalism, graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0, \, \forall e \in E$.

@@

\subsection{\algname{}: Generalized algorithm for agglomerative signed graph partitioning} \label{sec:algorithm}

In Algorithm \ref{main_alg}, we provide a simplified pseudo-code for the proposed \algname{} algorithm that is based on a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. The algorithm has two variants, depending on the boolean value of the input option \texttt{addCannotLinkConstraints}. The first one, with \texttt{addCannotLinkConstraints=False}, starts by merging clusters with the strongest attractive interaction and it stops when the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 3 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l | c | c  c}
            % \toprule\toprule
            \multicolumn{3}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

            \midrule
            % \cmidrule[0.3em]{2-6}
            % \morecmidrules \cmidrule[0.15em]{2-6}
            % \midrule \midrule
            % \multirow{5}{*}[-0.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact(S_u ,S_v)$}\end{turn}} 
             & Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ 
            % \cmidrule[0.07em]{2-6}

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the existing clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm \algname{}, given a linkage criteria, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_v) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}
\begin{figure}
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=0.9\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
% Only the involved segments are colored.
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}

@@

In the special case of an unsigned graph with only positive interactions, i.e. $w_e^-=0$ and $\cost_e \geq 0$ $\forall e\in E$, %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 the algorithm performs a standard agglomerative hierarchical clustering by returning only a single cluster and a hierarchy of clusters defined by the order in which the clusters are merged (see Table \ref{tab:linkage-criteria}, unsigned graphs).

### 2019-05-23 chapters/5_experiments_cityscapes.tex
Add Elke comments; squeeze for 1st submission

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and confirm our findings on neuron-segmentation: \algname{} with average linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs. Max.}, or under-cluster and merge instances, like \emph{Sum}. In Appendix, Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
\begin{figure}[t]
\centering
\begin{minipage}[T]{0.6\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the cityscapes validation set achieved by the tested pipelines.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.37\textwidth}
    \centering
\includegraphics[width=0.95\textwidth]{./figs/cityscapes_compare_2.pdf} % left bottom right top
\end{minipage}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: similarly to the previous experiments, \algname{} with \emph{Average} linkage achieves the best scores, whereas other linkage tend to over-cluster, like \emph{Abs. Max.}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\begin{figure}[t]
\centering
\begin{minipage}[b]{0.5\textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
           & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
          Pipeline & method & \textsc{No} & \textsc{Yes} \\ \midrule
DWT \cite{bai2017deep} & - & 21.2 & - \\
SGN \cite{liu2017sgn} & - & 29.2 & - \\
Mask RCNN \cite{he2017mask} & - & 31.5 & - \\ \hline
 & \textbf{\algname{} Avg-Link}& \textbf{34.3}  & 33.9  \\
\multirow{2}{*}{GMIS \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
 & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\
 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \captionof{table}{Average Precision (AP) scores (higher is better) on the CityScapes validation set.}
    \label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[b]{0.46\textwidth}
    \centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_3.pdf} % left bottom right top
\caption{Instance segmentations given by different \algname{} linkage criteria on CityScapes}\label{fig:cityscapes}
\end{minipage}
\end{figure}

### 2019-05-23 chapters/5_experiments_compare_rules.tex
Add Elke comments; squeeze for 1st submission

\subsection{Data: CREMI Challenge} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score\footnote{\url{https://cremi.org/leaderboard/}}, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{Additional methods tested } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.

>>>>

\subsection{Data and methods} \label{sec:cremi_challenge}
We evaluate the algorithms in our framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score (\url{https://cremi.org/leaderboard/}), based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

\textbf{State-of-the-art methods } We compare the performances of \algname{} with other basic and state-of-the-art post-processing methods. To ensure a fair comparison, we test all methods on the same predictions of our CNN model. As basic method, we perform a simple thresholding (THRESH) by running connected components on a boundary map generated from the CNN affinities (see Appendix \ref{sec:cremi_details} for more details on this and the following methods). On the other hand, most of state-of-the-art methods for neuron-segmentation first generates 2D superpixels and then apply a graph partitioning algorithm, since this approach so far proved to be the most reliable that could scale up to the size of the problem. Superpixels are usually computed with a watershed algorithm seeded at the maxima of a boundary distance transform (WSDT). The algorithms employed in our comparison to partition the superpixel graph were given by approximations of the multicut (WSDT+MC) and lifted multicut (WSDT+LMC) problems.
